Functional vs. Object Oriented Programming: Productivity comparison

### 2015-10-23 article.tex
changes

\title{Functional vs. Object Oriented Programming}
\author{Lorenzo Corneo and Nikolaos-Ektoras Anestos \\
	\{corneo, anestos\}@kth.se}
\date{\today}
\maketitle

@@

From the evaluation of the gathered data it is possible to see that, averagely, the number of Lines Of Code in a functional programming language is smaller than in an Object Oriented Programming language. As a consequence, Functional Programming allows an increased productivity (fewer lines of code correspond to a time saving).
\end{abstract}

@@

\begin{itemize}
\item FASTA
\item k-nucleotide
\item Mandelbrot
\item n-body
\item pi-digits
\item regex-dna
\item reverse-complement
\item spectral-norm
\end{itemize}

>>>>

\title{Functional vs. Object Oriented Programming: Productivity comparison}
\author{Lorenzo Corneo and Nikolaos-Ektoras Anestos \\
	\{corneo, anestos\}@kth.se}
\date{\today}
\maketitle

@@

From the evaluation of the gathered data it is possible to see that, averagely, the number of Lines Of Code in a functional programming language is smaller than in an Object Oriented Programming language. As a consequence, Functional Programming allows an increased productivity (fewer lines of code correspond to a time saving during development).
\end{abstract}

@@

\begin{itemize}
\item FASTA, generate and write random DNA sequences
\item k-nucleotide, repeatedly update hashtables and k-nucleotide strings
\item Mandelbrot, generate a Mandelbrot set and write a portable bitmap
\item n-body, perform an N-body simulation of the Jovian planets
\item pi-digits, calculate the digits of Pi with arbitrary-precision arithmetic
\item regex-dna, match DNA 8-mers and substitute nucleotides for IUB code
\item reverse-complement, read DNA sequences and write their reverse-complement
\item spectral-norm, calculate an eigenvalue using the power method
\end{itemize}
